paper

### 2019-01-03 Report/paper.tex
comit report

\documentclass[11pt]{article}

@@

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines

@@

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}

@@

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{Report}

@@

    \maketitle

    \(\title(Abstract)\)

    \begin{itemize}
\tightlist
\item
  \#TODO write some sentence about general motivation for bibliometric
  analysis
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \#TODO write a few centences about the most central findings
\end{itemize}

    \hypertarget{introduction}{%
\subsection{1. Introduction}\label{introduction}}

    \hypertarget{bibliometric-study-to-analyse-the-papers-published-in-the-proceeding-of-the-conferences-organized-by-the-international-learning-science-society.}{%
\subsection{Bibliometric study to analyse the papers published in the
Proceeding of the Conferences organized by the International Learning
Science
Society.}\label{bibliometric-study-to-analyse-the-papers-published-in-the-proceeding-of-the-conferences-organized-by-the-international-learning-science-society.}}

    \hypertarget{data-processing}{%
\subsection{2. Data Processing}\label{data-processing}}

@@

    \hypertarget{metadata}{%
\subsubsection{2.1 Metadata}\label{metadata}}

\hypertarget{extraction}{%
\paragraph{Extraction}\label{extraction}}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{k+kn}{import} \PY{n+nn}{os} 
        \PY{k+kn}{import} \PY{n+nn}{pandas} \PY{k+kn}{as} \PY{n+nn}{pd}
        \PY{n}{rootdir} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{data/papers}\PY{l+s+s1}{\PYZsq{}}
        \PY{n}{contents} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{i} \PY{o}{=} \PY{l+m+mi}{0}
        \PY{n}{source} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{errors} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{doc} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{year} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{k}{for} \PY{n}{subdir}\PY{p}{,} \PY{n}{dirs}\PY{p}{,} \PY{n}{files} \PY{o+ow}{in} \PY{n}{os}\PY{o}{.}\PY{n}{walk}\PY{p}{(}\PY{n}{rootdir}\PY{p}{)}\PY{p}{:}
            \PY{k}{for} \PY{n+nb}{file} \PY{o+ow}{in} \PY{n}{files}\PY{p}{:}
                \PY{k}{if} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{txt}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{in} \PY{n+nb}{file}\PY{p}{:}
                    \PY{n}{i} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                    \PY{n}{path} \PY{o}{=} \PY{n}{os}\PY{o}{.}\PY{n}{path}\PY{o}{.}\PY{n}{join}\PY{p}{(}\PY{n}{subdir}\PY{p}{,} \PY{n+nb}{file}\PY{p}{)}
                    \PY{k}{with} \PY{n+nb}{open}\PY{p}{(}\PY{n}{path}\PY{p}{)} \PY{k}{as} \PY{n+nb}{file}\PY{p}{:}
                        \PY{n}{doc}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{path}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZus{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{3}\PY{p}{]}\PY{p}{)}
                        \PY{n}{year}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n+nb}{int}\PY{p}{(}\PY{n}{path}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{/}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{6}\PY{p}{:}\PY{l+m+mi}{10}\PY{p}{]}\PY{p}{)}\PY{p}{)}
                        \PY{k}{try}\PY{p}{:}
                            \PY{n}{text} \PY{o}{=} \PY{n+nb}{file}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{p}{)}
                            \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{text}\PY{p}{)}\PY{o}{\PYZgt{}} \PY{l+m+mi}{10} \PY{p}{:}
                                \PY{n}{contents}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{text}\PY{p}{)}
                            \PY{n}{source}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{subdir}\PY{p}{[}\PY{n+nb}{len}\PY{p}{(}\PY{n}{rootdir}\PY{p}{)}\PY{p}{:}\PY{p}{]}\PY{p}{)}
                        \PY{k}{except}\PY{p}{:}
                            \PY{n}{name}\PY{p}{,} \PY{n}{message}\PY{p}{,} \PY{n}{content} \PY{o}{=} \PY{n}{sys}\PY{o}{.}\PY{n}{exc\PYZus{}info}\PY{p}{(}\PY{p}{)}
                            \PY{n}{errors}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{message}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{k}{print}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Number of papers is : \PYZob{}\PYZcb{}}\PY{l+s+s1}{\PYZsq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{contents}\PY{p}{)}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

@@

    \hypertarget{data-cleaning}{%
\subsection{Data Cleaning}\label{data-cleaning}}

    your part for the references universities parsing \ldots{}

    \hypertarget{text-preprocessing}{%
\subsubsection{Text preprocessing}\label{text-preprocessing}}

    From the pdf parser some of the documents were corrupted with some weird
caracters such as `\xe2\x80\x99s', white space strings \ldots{}

@@

\textbf{\emph{Lemmatization}} is a word variations to the root of the
word (e.g.~working, works, worked changed to work).
\textbf{\emph{Stemming}} is the process of reducing inflected and
derived words to their word stem, base or root form---generally a
written word form As the use of the stop words to reduce the BOW (bag of
words size we also used lemmatization and stemming to be able to reduce
the number of words without taking off any information)

@@

    \hypertarget{keywords-extraction}{%
\subsection{Keywords extraction}\label{keywords-extraction}}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}7}]:} \PY{n}{keywords\PYZus{}df} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{read\PYZus{}csv}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{keywords\PYZus{}final.csv}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}30}]:} \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
         \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n+nb}{list}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{7}\PY{p}{,}\PY{p}{)}
         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xticks}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{n+nb}{min}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,}\PY{n+nb}{max}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Distribution of the number of documents per year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_24_0.png}
    \end{center}
    { \hspace*{\fill} \\}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}33}]:} \PY{k+kn}{from} \PY{n+nn}{IPython.display} \PY{k+kn}{import} \PY{n}{Image}
         \PY{n}{Image}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{keywords\PYZus{}by\PYZus{}year.png}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

@@

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_26_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    We wanted then to know what are the trends of words for each specific
year, so we selected distinct words for each year, it means that we
selected for each year the words that were present for that year and
never for the others. We get the graph below. As we can see from the
graph, the most used word in the papers, more than 10\% of 2015 papers
uses the word `peer', more than 6\% of the papers uses the words
`building', `embodied' in 2016. In 2017 the most frequent keyword on is
`reponsive' and in 2018 `tools' is present with more than 6\%.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}37}]:} \PY{n}{Image}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{distinct\PYZus{}words.png}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

@@

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_28_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \hypertarget{document-clustering}{%
\subsection{Document Clustering}\label{document-clustering}}

@@

>>>>

    \documentclass[journal,twocolumn]{IEEEtran}
\usepackage[noadjust]{cite}

@@

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

\usepackage{mathptmx}
\usepackage{algorithm}\usepackage{algorithmic}

@@

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}
    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
    \definecolor{ansi-default-inverse-bg}{HTML}{000000}

@@

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{paper}

@@

\renewcommand{\figurename}{Figure}
\captionsetup{labelformat=simple}\title{Bibliometric Analysis of ICLS and CSCL research}
\author{\IEEEauthorblockN{Léonore Valentine Guillain, Nour Ghalia Abassi}\par
    \IEEEauthorblockA{EPFL}
}
\maketitle

\begin{abstract}
    \begin{itemize}
\item ~
  \section{TODO write some sentence about general motivation for
  bibliometric
  analysis}\label{todo-write-some-sentence-about-general-motivation-for-bibliometric-analysis}
\end{itemize}

@@

\begin{itemize}
\item ~
  \section{TODO write a few centences about the most central
  findings}\label{todo-write-a-few-centences-about-the-most-central-findings}
\end{itemize}
\end{abstract}
    \section{Introduction}\label{introduction}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum.

    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua \cite{article1}. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit
in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
Excepteur sint occaecat cupidatat non proident, sunt in culpa qui
officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat \cite{book1,booklet1,conference1}. Duis aute irure
dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum.

To illustrate how code, equations and figures are included in the
notebook, I include a simple technical section (section
\ref{illustrative-example}) below.

    \subsection{Data Processing}\label{data-processing}

@@

    \subsubsection{Metadata}\label{metadata}

\paragraph{Extraction}\label{extraction}

@@

@@

    \subsection{Data Cleaning}\label{data-cleaning}

    your part for the references universities parsing ...

    \subsubsection{Text preprocessing}\label{text-preprocessing}

    From the pdf parser some of the documents were corrupted with some weird
caracters such as , white space strings

@@

\textbf{\emph{Lemmatization}} is a word variations to the root of the
word (e.g. working, works, worked changed to work).
\textbf{\emph{Stemming}} is the process of reducing inflected and
derived words to their word stem, base or root form---generally a
written word form As the use of the stop words to reduce the BOW (bag of
words size we also used lemmatization and stemming to be able to reduce
the number of words without taking off any information)

@@

    \subsection{Keywords extraction}\label{keywords-extraction}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_27_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_29_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    We wanted then to know what are the trends of words for each specific
year, so we selected distinct words for each year, it means that we
selected for each year the words that were present for that year and
never for the others. We get the graph below. As we can see from the
graph, the most used word in the papers, more than 10\% of 2015 papers
uses the word 'peer', more than 6\% of the papers uses the words
'building', 'embodied' in 2016. In 2017 the most frequent keyword on is
'reponsive' and in 2018 'tools' is present with more than 6\%.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \subsection{Document Clustering}\label{document-clustering}

    \section{Illustrative Example}\label{illustrative-example}

For the purposes of illustration, consider a damped harmonic oscillator
driven by a sinusoidal signal:

\begin{equation}
\frac{\mathrm{d}^2x}{\mathrm{d}t^2} + 2\zeta\omega_0\frac{\mathrm{d}x}{\mathrm{d}t} + \omega_0^2x = A\sin(\omega t), \label{eq:problem}
\end{equation}

\noindent where \(x(t)\) is the quantity of interest, \(\zeta\) is the
damping constant, \(\omega_0\) is the undamped resonant frequency, and
\(A\sin(\omega t)\) is the driving sinusoidal signal. The steady state
solution to \eqref{eq:problem} is given by:

\begin{eqnarray}
x(t) &=& \frac{A}{Z_m\omega}\sin(\omega t + \phi), \label{eq:soln}\\
Z_m &=& \sqrt{(2\omega_0\zeta)^2+\frac{(\omega^2-\omega_0^2)^2}{\omega^2}}, \nonumber\\
\phi &=& \arctan\left(\frac{2\omega\omega_0\zeta}{\omega^2-\omega_0^2}\right). \nonumber
\end{eqnarray}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_40_0.png}\end{center}
        \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}
        \label{fig1}
    \end{figure}

    In Figure \ref{fig1} we plot the steady state amplitude of a 100 Hz
oscillator as a function of driving frequency. We see that the
oscillator exhibits a strong resonance for small values of \(\zeta\),
and that the resonance frequency is slightly lower than the driving
frequency of 100 Hz.

\begin{algorithm}
\caption{Calculate $y = x^n + z^m$}
\begin{algorithmic} 
\REQUIRE $n \geq 0 \vee x \neq 0 \vee z \geq 0 \vee m \neq 0$
\ENSURE $y = x^n + z^m$
\STATE $y \leftarrow 1$
\IF{$n < 0$}
  \STATE $N \leftarrow -n$
\ELSE
  \STATE $N \leftarrow n$
\ENDIF
\end{algorithmic}
\end{algorithm}
    \section{Conclusions}\label{conclusions}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum.

@@

\bibliographystyle{unsrt}
\bibliography{references}
